Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
updated Experiment Logistics section

@@

\noindent {\bfseries Experiment Execution Details} 
We plan to recruit from 200 users for the purpose of this study, 
making it largest user study to date examining Tor. 
This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
the censorship environments and will write a browser extension to 
log when user activity, such as what websites they were successfully able to visit. 
The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take less than an hour. 
Participants will be compensated \$30 for their time, 
which is more to cover minimum wage and transportation costs.  \\

>>>>

At the start of the study, participants will be informed
of the role they they will be playing in the study. Particularly,
they will be informed that they are in a censorship environment
which prevents them from visiting certain websites, but they
are people who would like to visit those websites for 
leisurely purposes.

@@

\noindent {\bfseries Experiment Logistics} 
The IRB protocol to run this user study has been approved (2014-12-6995). 
We plan to recruit from 100-200 users for the purpose of this study, 
making it largest user study to examine Tor.  This study will be conducted at the 
Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
censorship environments and will record computer screens to capture 
user activity. The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take about an hour. 
Participants will be compensated \$30 for their time, which is more to cover 
minimum wage for an hour and any transportation costs to the lab.  \\
